Discrete Quantum Theories and Computing

### 2018-12-02 dissertation.tex
dissertation.lyx Abstract Updating...

\begin{abstract*}\todo{Rewrite the abstract so that the committee
can sign it. Prof. Thurston: ``To address the same issue, the thesis
contains four different theories each have different pros and cons.
The abstract should said them separately and explicitly.'' }

Most quantum computing models are based on the continuum of real numbers,
while classical digital computers faithfully realize only discrete
computational models. Analog computers appear to be an option, but
in reality are far weaker than would be needed for computational models
requiring real numbers. One approach to resolving this conflict is
to find consistent mathematical ways to limit measurement precision
to computable contexts that do not require incomputable real numbers.
\todo{I don't understand the previous two sentences... Maybe simplify...
}Our goal is to build a more philosophically consistent models by
investigating discrete quantum computing using finite number systems,
and, alternatively, by incorporating finite precision measurement
using intervals into quantum theory.

@@

Our second framework employs only finite fields over prime numbers
of the form $4\ell+3$, which possess no solutions to $x^{2}+1=0$,
and thus permit an elegant complex representation of the finite field
by adjoining $\rmi=\sqrt{-1}$. Because the states of a discrete $n$-qubit
system are in principle enumerable, we can count the number of states,
and determine the proportions of entangled and unentangled states.
We tried define its measurement process in three different approaches.
For the model only predicting possible or impossible, we have solutions
to deterministic quantum algorithms such as Deutsch's algorithm, but
unnaturally strong computational power may still occur. In an improved
model, the probability of measurement results could be predicted locally.

the probabilistic Grover search algorithm can be implemented in a
local region, we haven't found a consistent way to treat quantum probability
measures in general.

@@

\tableofcontents{}\todo{Reorganize the chapters and sections to
fit the new abstract.}

@@

The cardinal probability over finite fields defined in Eq.~(\ref{eq:cardinalProbability})
is based on the conventional Born rule, Eq.~(\ref{eq:Born-ComputationalBasis}).
Although they are valid inside an ordered region, some quantum algorithms,
like Shor's~\cite{Shor1999,Mermin2007,Jaeger2007}, don't localize
their computation in a small region. Moreover, since we haven't found
a way to manipulate the resulting cardinal probabilities, we have
little idea how to define the mixed states and expectation values.
To overcome these issues, we try a different approach to define a
``conventional'' probability over finite fields axiomatically.

>>>>

\begin{abstract*}Most quantum computing models are based on the continuum
of real numbers, while classical digital computers faithfully realize
only discrete computational models. Analog computers appear to be
an option, but in reality are far weaker than would be needed for
computational models requiring real numbers. One approach to resolving
this conflict is to find consistent mathematical ways to limit measurement
precision to computable contexts that do not require incomputable
real numbers. Our goal is to build a more philosophically consistent
models by investigating discrete quantum computing using finite number
systems, and, alternatively, by incorporating finite precision measurement
using intervals into quantum theory.

@@

Our second framework employs only finite fields over prime numbers
of the form $4\ell+3$, which possess no solutions to $x^{2}+1=0$,
and thus permit an elegant complex representation of the finite field
by adjoining $\rmi=\sqrt{-1}$. Because the states of a discrete $n$-qubit
system are in principle enumerable, we can count the number of states,
and determine the proportions of entangled and unentangled states.
We tried define its measurement process in three different approaches.
For the model only predicting possible or impossible, we have solutions
to deterministic quantum algorithms such as Deutsch's algorithm, but
unnaturally strong computational power may still occur. In an improved
model, the cardinal probability of measurement results could be predicted
locally. In the local ordered region, the unnaturally computational
power is ruled out and the probabilistic Grover search algorithm can
be implemented. However, lacking arithmetic operations on cardinal
probabilities, expectation values cannot be defined easily. Since
arithmetic operations works with conventional probability measures,
we consider quantum probability measures over finite fields, but we
haven't found a consistent way to treat them in general.

@@

\tableofcontents{}\todo{Split Chapter~\ref{chap:DQT=000026DQC}
into ``Quantum Theories and Computing over Unrestricted Finite Fields''
and ``Quantum Theories and Computing over $\ff{p^{2}}$'' two chapters.
}

@@

The cardinal probability over finite fields defined in Eq.~(\ref{eq:cardinalProbability})
is based on the conventional Born rule, Eq.~(\ref{eq:Born-ComputationalBasis}).
Although they are valid inside an ordered region, some quantum algorithms,
like Shor's~\cite{Shor1999,Mermin2007,Jaeger2007}, don't localize
their computation in a small region. \todo{Remove the discussion
of Shor's algorithm if I cannot verify it on DQT(I) on time. }Moreover,
since we haven't found a way to manipulate the resulting cardinal
probabilities, we have little idea how to define the mixed states
and expectation values. To overcome these issues, we try a different
approach to define a ``conventional'' probability over finite fields
axiomatically.
